A Data-Driven Framework for Neural Field Modeling

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex

	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework. Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion. We have primarily developed the framework for higher density intracranial measurements. We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.}

	\emph{..., and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
considered. This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored. In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
    \end{enumerate}

    \subsection{Additional Comments}

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \item The use of Euler discretisation and how this affects the system's behavior.
        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.\\ \\
\emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points. The continuous field $v(\mathbf r)$ can be sampled using a field of Dirac-delta functions, $\delta(\mathbf r)$ located at the lattice points as
\begin{equation}
 v_s(\Delta J)=\sum_{J \in \mathbb Z^n}\delta(\mathbf r-\Delta J)v(\mathbf r)
\end{equation}
taking Fourier transfom of the sampled field $v_s(\Delta J)$ we have
\begin{align}
 V_s(\boldsymbol{\nu})&=\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n}\delta(\boldsymbol{\nu}-\frac{J}{\Delta})\ast V(\boldsymbol\nu)\\
&=\frac{1}{\Delta^n}V(\boldsymbol\nu)+\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n\setminus \mathbf \{0\}}V(\boldsymbol{\nu}-\frac{J}{\Delta})
\end{align}
hence,$V_s(\boldsymbol{\nu})$ contains $V(\boldsymbol\nu)$ plus infinitely many copies (aliases) of  $V(\boldsymbol\nu)$ repeated on the regular lattice $\left\lbrace \frac{J}{\Delta}; J\in \mathbb Z^n\right\rbrace$. Given the dynamic field is band-limited with a cut-off frequency $\boldsymbol\nu_c$ in order for $V(\boldsymbol\nu)$ to be disjointed with its aliases the amount of shift $\frac{1}{\Delta}$ must be at least $2\nu_c$, therefore
\begin{equation}\label{ap:Shannon}
 \Delta\le\frac{1}{2\rho\nu_c}
\end{equation}
where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. To recover the continuous field, we first introduce a low-pass filter \begin{equation}
F(\boldsymbol \nu)=\begin{cases}
  \Delta^n & |\boldsymbol\nu|\le \boldsymbol\nu_c \\
  0 & \text{otherwise}
\end{cases} 
\end{equation}
if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum can be recovered using
\begin{equation}
 V(\boldsymbol\nu)=F(\boldsymbol \nu)V_s(\boldsymbol\nu)
\end{equation}
taking inverse Fourier transform we have
\begin{align}
v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
&=\sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
\end{align}
However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the summ of weighted, spatially translated, continuous  basis functions.}

        \item The existing literature on inversion schemes for similar models of brain activity.
        \item In section 3, Table 6 is mentioned however there is no such table in the ms.
    \end{enumerate}

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex

	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework. Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion. We have primarily developed the framework for higher density intracranial measurements. We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.}

	\emph{..., and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
considered. This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored. In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
    \end{enumerate}

    \subsection{Additional Comments}

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.
        \item The use of Euler discretisation and how this affects the system's behavior.
        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.\\ \\
\emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points. The continuous field $v(\mathbf r)$ can be sampled using a field of Dirac-delta functions, $\delta(\mathbf r)$ located at the lattice points as
\begin{equation}
 v_s(\Delta J)=\sum_{J \in \mathbb Z^n}\delta(\mathbf r-\Delta J)v(\mathbf r)
\end{equation}
taking Fourier transfom of the sampled field $v_s(\Delta J)$ we have
\begin{align}
 V_s(\boldsymbol{\nu})&=\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n}\delta(\boldsymbol{\nu}-\frac{J}{\Delta})\ast V(\boldsymbol\nu)\\
&=\frac{1}{\Delta^n}V(\boldsymbol\nu)+\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n\setminus \mathbf \{0\}}V(\boldsymbol{\nu}-\frac{J}{\Delta})
\end{align}
hence,$V_s(\boldsymbol{\nu})$ contains $V(\boldsymbol\nu)$ plus infinitely many copies (aliases) of  $V(\boldsymbol\nu)$ repeated on the regular lattice $\left\lbrace \frac{J}{\Delta}; J\in \mathbb Z^n\right\rbrace$. Given the dynamic field is band-limited with a cut-off frequency $\boldsymbol\nu_c$ in order for $V(\boldsymbol\nu)$ to be disjointed with its aliases the amount of shift $\frac{1}{\Delta}$ must be at least $2\nu_c$, therefore
\begin{equation}\label{ap:Shannon}
 \Delta\le\frac{1}{2\rho\nu_c}
\end{equation}
where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. To recover the continuous field, we first introduce a low-pass filter \begin{equation}
F(\boldsymbol \nu)=\begin{cases}
  \Delta^n & |\boldsymbol\nu|\le \boldsymbol\nu_c \\
  0 & \text{otherwise}
\end{cases} 
\end{equation}
if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum, $V(\boldsymbol\nu)$ can be recovered using
\begin{equation}
 V(\boldsymbol\nu)=F(\boldsymbol \nu)V_s(\boldsymbol\nu)
\end{equation}
taking inverse Fourier transform we have
\begin{align}
v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
&=\sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
\end{align}
However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the sum of weighted, spatially translated, continuous  basis functions.}

### 2010-12-30 ltx/first_order_framework/response_to_reviews.tex

	\emph{In response to this important point, the authors have made an effort to be clear that we are not considering scalp EEG to be a valid data source for the estimation framework. Amendments have been made to the Introduction (last paragraph), Method (after equation 9), and Discussion. We have primarily developed the framework for higher density intracranial measurements. We believe that the spatial frequency response and sampling density of extracranial EEG/MEG measurements will be insufficient to estimate the connectivity structure.}

	\emph{..., and maybe we can say the framework can be altered in the case of scalp EEG by considering the lead field in the mapping between the membrane voltage and the electrophysiological data, resulting in different observation equation (if nonlinear we need unscented transform on observation and if not the state estimation remains unchanged.) This is from PLoS review which might be useful: In much of the previous papers cited the EEG/MEG lead field is
considered. This is different of course for scalp electrodes than for intracranial electrodes but should be explicitly spelled out because this factor cannot be ignored. In fact the observation model is not quite realistic, without lead field and without amplifier characteristics.}
    \end{enumerate}

    \subsection{Additional Comments}

    \begin{enumerate}
        \item The discrepancy of the results in Experiment II where the weights of the basis functions are not in agreement with the actual parameters while the reconstructed kernels seem satisfying.

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.''}

        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.

\emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points. The continuous field $v(\mathbf r)$ can be sampled using a field of Dirac-delta functions, $\delta(\mathbf r)$ located at the lattice points as
\begin{equation}
 v_s(\Delta J)=\sum_{J \in \mathbb Z^n}\delta(\mathbf r-\Delta J)v(\mathbf r)
\end{equation}
taking Fourier transfom of the sampled field $v_s(\Delta J)$ we have
\begin{align}
 V_s(\boldsymbol{\nu})&=\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n}\delta(\boldsymbol{\nu}-\frac{J}{\Delta})\ast V(\boldsymbol\nu)\\
&=\frac{1}{\Delta^n}V(\boldsymbol\nu)+\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n\setminus \mathbf \{0\}}V(\boldsymbol{\nu}-\frac{J}{\Delta})
\end{align}
hence,$V_s(\boldsymbol{\nu})$ contains $V(\boldsymbol\nu)$ plus infinitely many copies (aliases) of  $V(\boldsymbol\nu)$ repeated on the regular lattice $\left\lbrace \frac{J}{\Delta}; J\in \mathbb Z^n\right\rbrace$. Given the dynamic field is band-limited with a cut-off frequency $\boldsymbol\nu_c$ in order for $V(\boldsymbol\nu)$ to be disjointed with its aliases the amount of shift $\frac{1}{\Delta}$ must be at least $2\nu_c$, therefore
\begin{equation}\label{ap:Shannon}
 \Delta\le\frac{1}{2\rho\nu_c}
\end{equation}
where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. To recover the continuous field, we first introduce a low-pass filter \begin{equation}
F(\boldsymbol \nu)=\begin{cases}
  \Delta^n & |\boldsymbol\nu|\le \boldsymbol\nu_c \\
  0 & \text{otherwise}
\end{cases} 
\end{equation}
if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum, $V(\boldsymbol\nu)$ can be recovered using
\begin{equation}
 V(\boldsymbol\nu)=F(\boldsymbol \nu)V_s(\boldsymbol\nu)
\end{equation}
taking inverse Fourier transform we have
\begin{align}
v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
&=\sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
\end{align}
However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the sum of weighted, spatially translated, continuous  basis functions.}

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex

        \item The use of Euler discretisation and how this affects the system's behavior.

		\emph{This point was made by a reviewer from our PLoS attempt. The reviewer stated: ``1. The authors might want to reference prior work in using Kalman
		Filtering for the estimation of neural mass models from data [1-3],
		[13]. In fact from those papers stressed the importance of carrying out
		a high order discretization of the differential equations, which should
		be in fact treated as stochastic. In equation (S1.1) of the extended
		derivation, it is shown that an Euler approximation is taken which may
		even change the dynamical properties of the system. The authors should
		discuss this issue.''}

        \item The derivation of Equations (30) and (31) [spacing of basis functions] and make them more transparent for the general audience.

\emph{Consider a regular lattice in $\mathbb R^n$, with lattice points $\left\lbrace \Delta J; J\in \mathbb Z^n\right\rbrace$ and where $\Delta$ is the distance between adjacent points. The continuous field $v(\mathbf r)$ can be sampled using a field of Dirac-delta functions, $\delta(\mathbf r)$ located at the lattice points as
\begin{equation}
 v_s(\Delta J)=\sum_{J \in \mathbb Z^n}\delta(\mathbf r-\Delta J)v(\mathbf r)
\end{equation}
taking Fourier transform of the sampled field $v_s(\Delta J)$ we have
\begin{align}
 V_s(\boldsymbol{\nu})&=\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n}\delta(\boldsymbol{\nu}-\frac{J}{\Delta})\ast V(\boldsymbol\nu)\\
&=\frac{1}{\Delta^n}V(\boldsymbol\nu)+\frac{1}{\Delta^n}\sum_{J\in\mathbb Z^n\setminus \mathbf \{0\}}V(\boldsymbol{\nu}-\frac{J}{\Delta})
\end{align}
hence,$V_s(\boldsymbol{\nu})$ contains $V(\boldsymbol\nu)$ plus infinitely many copies (aliases) of  $V(\boldsymbol\nu)$ repeated on the regular lattice $\left\lbrace \frac{J}{\Delta}; J\in \mathbb Z^n\right\rbrace$. Given the dynamic field is band-limited with a cut-off frequency $\boldsymbol\nu_c$ in order for $V(\boldsymbol\nu)$ to be disjointed with its aliases the amount of shift $\frac{1}{\Delta}$ must be at least $2\nu_c$, therefore
\begin{equation}\label{ap:Shannon}
	\Delta\le\frac{1}{2\rho\nu_c}
\end{equation}
where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. To recover the continuous field, we first introduce a low-pass filter \begin{equation}
F(\boldsymbol \nu)=\begin{cases}
  \Delta^n & |\boldsymbol\nu|\le \boldsymbol\nu_c \\
0 & \text{otherwise}
\end{cases} 
\end{equation}
if the sampling rule \eqref{ap:Shannon} is satisfied, the original spectrum, $V(\boldsymbol\nu)$ can be recovered using
\begin{equation}
	V(\boldsymbol\nu)=F(\boldsymbol \nu)V_s(\boldsymbol\nu)
\end{equation}
taking inverse Fourier transform we have
\begin{align}
	v(\mathbf s)&=f(\mathbf s)\ast v_s(\Delta J) \\
	&= \sum_{J \in \mathbb Z^n}f(\mathbf s-\Delta J) v_s(\Delta J)
\end{align}
However many other basis functions can be potentially used for reconstruction, and a continuous field can be reconstructed from the sampled field by the sum of weighted, spatially translated, continuous  basis functions.}

Parham: I made a copy for my edits so that we don't get conflicts.

\emph{Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$. The observations can be considered samples from a continuous field that is filtered (convolved) by the observation kernel as
\begin{equation}
	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation} 
where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
\begin{align}
 Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
\end{align} 
It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice with spacing $\frac{1}{\Delta_y}$. Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$. In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\frac{1}{\Delta_y}$ must be at least $2\boldsymbol\nu_{cy}$ (since each alias has a spectral range of
\begin{equation}
	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
\end{equation}
Therefore, to avoid aliasing the distance between observations must satisfy
\begin{equation}\label{eq:SamplingCriteria}
	\frac{1}{\Delta_y} \ge 2\nu_{cy}.
\end{equation}
Since the observation kernel is not an ideal filter an oversampling parameter should be included to further separate the aliases. Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
\begin{equation}\label{ap:Shannon}
	\Delta_y\le\frac{1}{2\rho\nu_{cy}},
\end{equation}
where $\rho \in \mathbb{R} \ge 1$. }

### 2010-12-31 ltx/first_order_framework/response_to_reviews.tex

Parham: I made a copy for my edits so that we don't get conflicts.

\emph{Consider the cortical sheet defined on the surface $\Omega$ with the sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$. The observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
\begin{equation}
	y(\mathbf{r}_n)=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation} 
where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The Fourier transform of $y(\mathbf{r}_n)$ is
\begin{align}
 Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu)+\frac{1}{\Delta_y^2}\sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{n}{\Delta_y}\right).
\end{align} 
It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-2$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice centered at $n\Delta_y^{-1}$. Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$. In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
\begin{equation}
	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
\end{equation}
Therefore, to avoid aliasing the distance between observations must satisfy
\begin{equation}\label{eq:SamplingCriteria}
	\frac{1}{\Delta_y} \ge 2\nu_{cy}.
\end{equation}
Since the observation kernel is not an ideal filter an oversampling parameter should be included to further separate the aliases. Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
\begin{equation}\label{ap:Shannon}
	\Delta_y\le\frac{1}{2\rho\nu_{cy}},
\end{equation}
where $\rho \in \mathbb{R} \ge 1$. }

### 2010-12-31 ltx/first_order_framework/LaTeX_Manuscript.tex
small edit to derivation for Shannons sampling

The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf{y}_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \varepsilon_t(\mathbf{r}_n), 
\end{equation}
where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=1,...,n_y$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$. \dean{(for reviewer 1, comment 3:) Note, since we are considering intracranial measurements recorded directly from the surface or within the cortex the lead field is not modeled by the observation equation.}

>>>>

The mapping between the membrane voltage and the electrophysiological data, denoted by $\mathbf{y}_t$, is modelled using the observation function that incorporates sensors with a spatial extent by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_n) = \int_{\Omega} { m\left(\mathbf{r}_n-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, d\mathbf{r}'} + \varepsilon_t(\mathbf{r}_n), 
\end{equation}
where $m\left(\mathbf{r}_n-\mathbf{r}'\right)$ is the observation kernel, $\mathbf{r}_n$ defines the location of the electrodes in the field, $n=0,...,n_y-1$ indexes the sensors and $\varepsilon_t(\mathbf{r}_n) \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes a multivariate normal distribution with mean zero and the covariance matrix $\boldsymbol{\Sigma}_{\varepsilon} = \sigma_{\varepsilon}^2\mathbf{I}$. \dean{(for reviewer 1, comment 3:) Note, since we are considering intracranial measurements recorded directly from the surface or within the cortex the lead field is not modeled by the observation equation.}
